Supplementary methods

### 2020-08-24 text/supplemental_methods.Rmd
moved survival figure to where the figure legend is in the supplement. Updated text

### Survival

@@

**supplementary figure SM2** gives a comparison on log-scale between
the post-fit survival curves and the CDC data it is based on.

>>>>

@@

### Survival
```{r child='../code/figureSM2.Rmd'}
```

**supplementary figure SM2** gives a comparison between the post-fit
survival curves for men and women vs the CDC data it is based on. This
comparison does not distinguish on ethnicity for simplicity in
visualization.
